### 2019-12-10 ack.tex
update

Hello there! Did you stumble across this phrase by accident, 
or are you looking for what I think you're looking for?
For every page you turn over in this book,
I feel that there is at least one person who deserves to be thanked 
a thousand times over for their continued love, sacrifices and support.
So here we go, until the end of the book: Thank you! Thank you!
Thank you! Thank you! Thank you! Thank you! Thank you! Thank you! 
Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!
Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!
Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!
Thank you! Thank you! Okay, enough with the silly business.
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Yvan, you are an incredible supervisor and group leader. 
You always tell the baby PhD students that the first step in a PhD
is not learning to write well, but learning to like to write.
Those words are amazing PhD training wheels.
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Katleen, thank you for your dedication and perseverance
in guiding me and making sure I got off to a good start in my PhD.
I see exciting times ahead for the KDP group, which is overflowing
with enthusiasm and inspiration. I wonder what the future will bring!
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Frank, thank you for giving me the opportunity to start on this journey.
You are an inexhaustible source of new ideas
which often explore the very thin line
between ingenuity and completely insane.
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Jo, sorry for spilling coffee on your shoes on my first day in Blok B.
My strategy seemed to have worked, for suddenly I had a fourth promotor!
I thoroughly enjoyed my time as an unofficial member of your group.
You are a true people's person; you bring out the best in everybody.
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Joeri, we've come full circle. You started me on this adventure
with your incredible friendliness and that darned oversized pumpkin;
and now, with you as my jury member, you helped me reach my goal.
Let's stay in touch :)
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Wouter, I cannot imagine a better partner to do a PhD with.
If we were genes, I'm sure we would reciprocal activators,
constantly stimulating each other to do just a little bit more!
Yet, our knowledge was often so perfectly complementary;
if we were a PCA plot, you'd be PC1 and I'd be PC2.
Or maybe the other way around? Let's take turns being PC1 and PC2.
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Sofie, you saved my rear-end from embarrassing moments more frequently than I dare to admit.
The perfect example was when I walked in the MMM on 2014-01-06,
I arrived a little bit too late, and you send me a message:
"You do know that you have to present today, right?"
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Helena, thank you for being such a lovely colleague and an even better friend.
I enjoy our scientific talks and our non-scientific walks. 
Together with you, I played the longest ongoing game of hide-and-seek,
on page 22-9 you probably already found the truc that I am referring to.
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Paulina, like a soft summer wind you passed through our lives.
Thanks for putting so many healthy vege-tables and strange Polish delicacies in our fridge,
for cycling together to work, and for making weird noises at Remi.
I'm looking forward to the next time we meet, so you can be amazed at how much Remi has grown.
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Soup: Dani, Helena, Caroline, Robin B, Maxim, Annelies, Quentin, Katrien, Arne G, Ruth, Joris
Dambi
Dambi
Dambi
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Miriam
Miriam
Miriam
Miriam
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Laure, Michael, Jasper en Lize (spelling??)
Mara, Seppe \& Alice
Marta, Jan, Tristan, Rafael
Daan, Mieke \& Lou
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Cedric
Cedric
Cedric
Cedric
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Familie
Familie
Familie
Familie
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Victor, humor
Victor
Victor
Victor
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Hendrik, getting into PC
Hendrik 
Hendrik
Hendrik
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Papa Chris, babbel voor het slapen gaan, de vele schaakspelletjes
Chris
Chris
Chris
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Mama en papa Jean-Paul: opvoeding, zorgeloosheid
Mama
Mama
Mama
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Amor, as I write this, you are sitting on my lap and drooling on the table.
I guesstimate about 50\% of this dissertation was written like this.
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Hello Petit Remi! 
Remi
Remi
Remi
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Dear Caro,
I cannot imagine a better partner and mother than you.
You are a strange combination of being extremely thoughtful and caring,
yet you roll over laughing when I stub my toe against the side of the table.
Let's get back on track collecting doorsteps,
and spending time doing the things we love, just us three.
I look forward to the rest of our lives together,
my strong independent woman.

>>>>

Hello there! Did you stumble across this phrase by accident,\\or are you looking for what I think you're looking for?
For every page you turn over in this book,\\I feel that there is at least one person who deserves to be thanked 
a thousand times over for their continued love, sacrifices and support.\\So here we go, until the end of the book: Thank you! Thank you!
Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!\\Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!
Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!\\Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!
Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!\\Okay, enough with the silly business. 
Go to the next chapter for more acknowledgements.

Yvan, you are an incredible supervisor and group leader.\\You always tell the baby PhD students that the first step in a PhD
is not learning to write well, but learning to like to write.\\Those words are amazing PhD training wheels.
Katleen, thank you for your dedication and perseverance\\in guiding me and making sure I got off to a good start in my PhD.
I see exciting times ahead for the KDP group, which is overflowing\\with enthusiasm and inspiration. I wonder what the future will bring!
Frank, thank you for giving me the opportunity to start on this journey.\\You are an inexhaustible source of new ideas
which often explore the very thin line\\between ingenuity and complete insanity.
Jo, sorry for spilling coffee on your shoes on my first day in Blok B.\\My strategy seemed to have worked, for suddenly I had a fourth promotor!
I thoroughly enjoyed my time as an unofficial member of your group.\\You are a true people's person; you bring out the best in everybody.
Joeri, you brought me into this whole adventure\\with your incredible friendliness and that darned oversized pumpkin;
and now, with you as my jury member, you helped me finish my PhD adventure.\\We've truly come full circle.
Go to the next chapter for more acknowledgements.

Wouter, I cannot imagine a better partner to do a PhD with. If we were genes,\\we'd be reciprocal activators, constantly stimulating each other to do just a little bit more!
Yet, our knowledge was often so perfectly complementary; if we were a PCA plot,\\you'd be PC1 and I'd be PC2. Or the other way around? Let's take turns being PC1 and PC2.
Sofie, you saved my rear-end from embarrassing moments more frequently than I dare\\ to admit. The perfect example was when I walked in the MMM on 2014-01-06,
I arrived a little bit too late, and you send me a message:\\"You do know that you have to present today, right?"
Helena, thank you for being such a lovely colleague and an even better friend.\\I enjoy our scientific talks and our non-scientific walks.
Together with you, I played the longest ongoing game of hide-and-seek,\\on page 22-9 you probably already found the truc that I am referring to.
Paulina, like a soft summer wind you passed through our lives.\\Thanks for putting so many healthy “vege-tables” and strange Polish delicacies in our fridge,
for cycling together to work, and for making weird noises at Remi.\\I look forward to the next time we meet; you will be amazed at how much Remi has grown.
A big thank you to all the Dambini's for taking care of me while I was hard at work:\\An,ArS,ArG,Art,C,D,H,I,Ja,Jon,Jor,Ka,Ke,Li,Lo,M,N,Pa,Pi,Q,RVd,RB,Ru,Sa,Sl,So,St,W,Y.
I'm grateful to be part of such a dynamic and fun group;\\you make hard work at the VIB feel like a walk in the park.
Go to the next chapter for more acknowledgements.

Because relaxing is as important as work,\\a special thanks to a selection of the friends and family.
Laure, Michael, Jasper \& Lize, thank you for the haut cuisine fun veggie nights.
Joke, Niels \& Kai, thank you for exploring dungeons with trolls and lizards together.
Marta, Jan, Tristan \& Rafaël, thank you for the many tasty brunches and classy parties.
Mara Marrainne, Sepperd \& Alice, thank you for all\\the unforgettable family moments with our cute kids.
Daan, Mieke \& Lou, thank you for taking matters in your own hands\\and upgrading our friendship status into family.
Sophie and Marc, thank youfor entertaining Caro\\while Elias, Charlotte and I play Minecraft together. 
Bart, thank you for being such a good friend\\and listening to me when I needed it the most.
Miriam, thank you for always being there for us,\\during the good times but also during times of need.
As part of our family, there will always be a spot for you in our house.\\Let it be a while until one of us has to organise another reception.
Cedric, no time difference or distance can keep us apart,\\or change our habit to forget the world during our gaming and conversations. 
놀라운 사람과 최고의 친구가되어 주셔서 감사합니다
Big hugs for my family who supported me (Vanessa, Marilou, Franco, Alain,\\Luc, Malika, Sien, Silke, Liam, Anne, Patrick, Evelyne, Stefaan, Arne, Laure, 
Paul, Tania, Dorian, Steven, Joke, Lukas, Lise), and often had to miss me at family parties.
To mama and papa Jean Paul, thank you for all your love.\\You gave me a carefree youth and a good set of morals,
and allowed me to study for as long as I liked.\\For all these things and so much more, I can never repay you.
Papa Chris, I always enjoy talking to you, such as the countless\\chess games that we played, and the late night discussions by my bedside.
You made me think for myself and have an opinion of my own.\\At the right time, I will pass on the torch to Remi.
Victor, you're the most adventurous of us three brothers.\\Maybe you don't know yet what life will bring, and that's okay. None of us do.
I enjoy driving other people absolutely nuts with our crazy talk.\\Thanks for all the memes :)
Hendrik, as the one who I always looked up to, I blame you for getting me interested\\in computers. With you taking computers apart on the table, how could I resist.
I know you paid dearly for this, though, since you would continuously have to\\repair the \textit{Windows Me} installation that I just destroyed.
Ingeborg, Elke and Gallina, thank you for your hospitality and tasty food.\\You are all amazing women
for all I know, dealing with a Cannoodt,\\requires a special kind of patience.
Go to the next chapter for more acknowledgements.

To Amor, a big thank you for contributing countless cuddles and endless drool.\\I guesstimate at least 50\% of the dissertation was written with you on my lap.

Hello Petit Remi! You're only seven months old,\\but it feels like I've known you for much longer already.
Your spontaneous happiness when you see me come downstairs\\from a hard day of work immediately makes my day.
Dear Caro, I cannot imagine a better partner and mother than you.\\You make me want to be the best version of myself.
Let's get back on track collecting doorsteps, and spending time doing the things we love,\\just us three. I look forward to the rest of my life together with my strong independent woman.

1

### 2019-12-10 boek.tex
update
update acks

%\usepackage[paperheight=24cm,paperwidth=17cm,margin=1.5cm,inner=2cm,outer=1.5cm]{geometry}
%\usepackage[
%	% set width and height to a4 width and height + 6mm
%	%width=16truecm, height=24truecm,
%	a4,
%	% use any combination of these options to add different cut markings
%	cam, axes, frame, cross,
%	% set the type of TeX renderer you use
%	pdftex,
%	% center the contents
%	center
%]{crop}

\usepackage[paperheight=24cm,paperwidth=17cm,margin=1.5cm,inner=2cm,outer=1.5cm]{geometry}
% adjust margins (should be done before importing fancyhdr!) %lmargin=2.5cm,rmargin=4cm,tmargin=3cm,bmargin=3cm

% text packages
\usepackage{csquotes}
\usepackage[english]{babel}
\usepackage{setspace}

@@

\newcounter{acki}
\setcounter{acki}{1}
\newcommand{\doack}{%
%	{\footnotesize %
%    %\#\theacki\ | % LINENUMBER DEBUG
%		\partialinput{\theacki}{\theacki}{ack}
%	}%
	\stepcounter{acki}%
}

@@

\fancypagestyle{mainmatter}{%    
	\fancyhf{} 	
	\fancyhead[RO,LE]{\nouppercase{\small \textsf{\leftmark}}}
	\fancyfoot[RO,LE]{\textsf{{\footnotesize Page \thepage}}}
	\fancyfoot[LO]{\ifodd\theacki\doack\fi}
	\fancyfoot[RE]{\ifodd\theacki\else\doack\fi}

}
\setlength{\headheight}{15pt}

@@

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} A common problem of pioneering computational tools is that during their development, there are rarely sufficient datasets available for adequately quantitatively assessing its performance. \\
	\textbf{Results:} We developed \texttt{dyngen}, a multi-modality simulator of single cells. 
	In \texttt{dyngen}, the biomolecular state of an \textit{in silico} cell changes over time according to a set of reactions defined by the cell's gene regulatory network. By simulating single cells in terms of its biomolecular state and reactions, the simulator is easily extendible for adding new modalities or experimental procedures. We demonstrate \texttt{dyngen}'s flexibility by simulating snapshot, time-series and perturbation experiments.\\
	\textbf{Conclusion:} \texttt{dyngen} lays the foundations for benchmarking a wide variety of computational single-cell tools, and can be used to help kick-start the development of future types of analyses.
\end{quote}

\vfill
{\large \textbf{Publication status}}
\begin{quote}
	Manuscript in preparation. \\
	\textbf{Cannoodt R}$^*$, Saelens W$^*$, Deconinck L, and Saeys Y.  \\
	{\footnotesize $^*$ Equal contribution}
\end{quote}

\vfill
{\large \textbf{Author contributions}}
\begin{quote}
	$\bullet$ \textbf{R.C.} and W.S. designed the study.\\
	$\bullet$ \textbf{R.C.}, W.S., and L.D. performed the experiments and analysed the data.\\
	$\bullet$ \textbf{R.C.} and W.S. implemented software packages.\\
	$\bullet$ \textbf{R.C.} and W.S. wrote the original manuscript.\\
	$\bullet$ \textbf{R.C.}, W.S., L.D., and Y.S. reviewed and edited the manuscript. \\
	$\bullet$ Y.S. supervised the project.
\end{quote}

@@

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} 
	Recent advances in single-cell RNA-sequencing allow modelling progression of single cells along a dynamic process of interest as a trajectory. While already more than 75 trajectory inference methods have been developed, comprehensive benchmarking demonstrated that pseudotemporal ordering cells robustly is still a challenging task.\\
	\textbf{Results:} \texttt{SCORPIUS} is a trajectory inference method specialised in pseudotemporally ordering single-cell profiles. Applying \texttt{SCORPIUS} to a large collection of datasets shows that it consistently produces more accurate and robust trajectories in comparison to state-of-the-art trajectory inference methods. We used \texttt{SCORPIUS} to generate novel hypotheses regarding dendritic cell development, which were subsequently validated \textit{in vivo}.\\
	\textbf{Conclusion:} By providing a robust and accurate toolkit for inferring linear trajectories, we aim to make pseudotime analysis as easy-to-use and prevalent as other types of analysis such as differential expression and gene set enrichment.
\end{quote}

@@

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} Recent technological advances allow studying dynamic processes by computationally ordering single-cell omics profiles along a trajectory. Since 2014, at least 75 tools for trajectory inference have been developed. For end-users, however, these methods are difficult to execute and compare, mainly due to high variability in input/output data structures, software requirements, and programming interfaces. \\
	\textbf{Results:} We developed \texttt{dyno}, a toolkit for inferring, visualising and interpreting single-cell trajectories, giving access to more than 50 TI methods. \texttt{dyno} provides downstream analyses such as visualising the trajectory with dot-plots or heatmaps, automated labelling using gene sets, automated inference of the directionality, and detecting genes that are differentially expressed along the trajectory. \\
	\textbf{Conclusion:} By providing a uniform interface for executing and visualising trajectories of 50 methods, \texttt{dyno} allows inferring and comparing trajectories for a much broader audience than previously possible.
\end{quote}

@@

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} Network inference methods are computational tools which use large omics datasets to predict which genes are regulated by which transcription factors.
	Since regulatory interactions are context-dependent, attempting to model regulatory dynamics in the form of a single regulatory network may have little relevance. \\
	\textbf{Results:} In this work, we introduce \texttt{bred}, the first algorithm for inferring case-wise regulatory networks. We generate . Analysing case-wise regulatory networks of 14'963 profiles from The Cancer Genome Atlas project demonstrated that regulatory interactions are often specific to particular cancer types, but can also be shared between several cancer types. \\
	\textbf{Conclusion:} Ultimately, this analysis has resulted in a list of candidate oncogenic genes and interactions per cancer type, though further analysis and validation is required to confirm their oncogenicity.
\end{quote}
% TODO: fix abstract
\vfill
{\large \textbf{Publication status}}
\begin{quote}
	Manuscript in preparation. \\
	\textbf{Cannoodt R}, Saeys Y$^*$, and De Preter K$^*$. \\
	{\footnotesize $^*$ Equal contribution}
\end{quote}

@@

\ifrenderall
\newpage
\graphicspath{{./ch6_bred/}}
\include{ch6_bred/content}
\fi 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH8: INCGRAPH       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{incgraph: Optimising regulatory networks} 
\chaptermark{incgraph: Optimising regulatory networks.} % short title
\label{chap:incgraph}

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} Graphlets are small network patterns that can be counted in order to characterise the structure of a network (topology). Counting graphlet can used to iteratively optimise a network in order to achieve certain topological properties.
	Up until now, however, graphlets were not suited as a metric for performing topology optimisation; when millions of minor changes are made to the network structure it becomes computationally intractable to recalculate all the graphlet counts for each of the edge modifications. \\
	\textbf{Results:} IncGraph calculates the differences in graphlet counts with respect to the network in its previous state.
	IncGraph reduces the execution time by several orders of magnitude when compared to recounting the graphlet counts from scratch at every iteration.
	We demonstrate the usefulness of this approach optimising gene regulatory networks using a graphlet-based fitness score. \\
	\textbf{Conclusion:} IncGraph is able to quickly quantify the topological impact of small changes to a network, which opens novel research opportunities to study changes in topologies in evolving or online networks, or develop graphlet-based criteria for topology optimisation.
\end{quote}

@@

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} In computational biology and other sciences, researchers are frequently faced with a choice between several computational methods for performing data analyses. Benchmarking studies aim to rigorously compare the performance of different methods using well-characterized benchmark datasets, to determine the strengths of each method or to provide recommendations regarding suitable choices of methods for an analysis. However, benchmarking studies must be carefully designed and implemented to provide accurate, unbiased, and informative results. \\
	\textbf{Results:}  Here, we summarise key practical guidelines and recommendations for performing high-quality benchmarking analyses, based on our experiences in computational biology. Our review spans the full pipeline of benchmarking, from defining the scope to best practices for reproducibility. This includes crucial questions regarding design and evaluation principles. \\
	\textbf{Conclusion:} With this review, we aim to guide computational researchers in avoiding common pitfalls in designing, performing, and interpreting benchmarks.
\end{quote}

>>>>

\usepackage[paperheight=24cm,paperwidth=17cm,margin=1.5cm,inner=2cm,outer=1.5cm]{geometry}
\usepackage[
	% set width and height to a4 width and height + 6mm
	%width=16truecm, height=24truecm,
	a4,
	% use any combination of these options to add different cut markings
	cam, axes, frame, cross,
	% set the type of TeX renderer you use
	pdftex,
	% center the contents
	center
]{crop}

%\usepackage[paperheight=24cm,paperwidth=17cm,margin=1.5cm,inner=2cm,outer=1.5cm]{geometry}
% adjust margins (should be done before importing fancyhdr!) %lmargin=2.5cm,rmargin=4cm,tmargin=3cm,bmargin=3cm

% text packages
\usepackage{csquotes}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{kotex} % hangul

@@

%\#\theacki\ | % LINENUMBER DEBUG
\newcounter{acki}
\setcounter{acki}{1}

\usepackage{makecell}
\newcommand{\doackl}{%
	\textcolor{med-gray}{\footnotesize\makecell[l]{\hspace*{-1.06em}\partialinput{\theacki}{\theacki}{ack}}}%
	\stepcounter{acki}%
}
\newcommand{\doackr}{%
\textcolor{med-gray}{\footnotesize\makecell[r]{\partialinput{\theacki}{\theacki}{ack}}}%
\stepcounter{acki}%
}

%\newcommand{\doack}[1]{%
%	\footnotesize\makecell[#1]{\partialinput{\theacki}{\theacki}{ack}}%
%	\stepcounter{acki}%
%}

\newcommand{\newperson}{\rule{10cm}{0.4pt}}

@@

\fancypagestyle{mainmatter}{%    
	\fancyhf{} 	
	\fancyhead[RO,LE]{\nouppercase{\small \textsf{\leftmark}}}
	\fancyfoot[RO,LE]{\textsf{{\footnotesize Page \thepage}}}
	\fancyfoot[LO]{\ifodd\theacki\else\doackl\fi}
	\fancyfoot[RE]{\ifodd\theacki\doackr\fi}
}
\setlength{\headheight}{15pt}

@@

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} A common problem of pioneering computational tools is that during their development, there are rarely sufficient datasets available for adequately quantitatively assessing its performance. \\
	\textbf{Results:} We developed dyngen, a multi-modality simulator of single cells. In dyngen, the biomolecular state of an \textit{in silico} cell changes over time according to a gene regulatory network. The simulator is extendible for adding new modalities or experimental procedures. We demonstrate dyngen's flexibility by applying it to benchmark RNA velocity and casewise network inference methods. \\
	\textbf{Conclusion:} dyngen lays the foundations for benchmarking a wide variety of computational single-cell tools and can be used to help kick-start the development of future types of analyses.
\end{quote}
%
%\vfill
{\large \textbf{Publication status}}
\begin{quote}
	Manuscript in preparation. \\
	\textbf{Cannoodt R}$^*$, Saelens W$^*$, Deconinck L, and Saeys Y.  \\
	{\footnotesize $^*$ Equal contribution}
\end{quote}
%
%\vfill
{\large \textbf{Author contributions}}
\begin{quote}
	$\bullet$ \textbf{R.C.} and W.S. designed the study.\\
	$\bullet$ \textbf{R.C.}, W.S., and L.D. performed the experiments and analysed the data.\\
	$\bullet$ \textbf{R.C.} and W.S. implemented software packages.\\
	$\bullet$ \textbf{R.C.} and W.S. wrote the original manuscript.\\
	$\bullet$ \textbf{R.C.}, W.S., L.D., and Y.S. reviewed and edited the manuscript. \\
	$\bullet$ Y.S. supervised the project.
\end{quote}

@@

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} 
	Recent advances in single-cell RNA-sequencing allow modelling progression of single cells along a dynamic process of interest as a trajectory. While already more than 75 trajectory inference methods have been developed, comprehensive benchmarking demonstrated that pseudotemporal ordering cells robustly is still a challenging task.\\
	\textbf{Results:} {SCORPIUS} is a trajectory inference method specialised in pseudotemporally ordering single-cell profiles. Applying {SCORPIUS} to a large collection of datasets shows that it consistently produces more accurate and robust trajectories in comparison to state-of-the-art trajectory inference methods. We used {SCORPIUS} to generate novel hypotheses regarding dendritic cell development, which were subsequently validated \textit{in vivo}.\\
	\textbf{Conclusion:} By providing a robust and accurate toolkit for inferring linear trajectories, we aim to make pseudotime analysis as easy-to-use and prevalent as other types of analysis such as differential expression and gene set enrichment.
\end{quote}

@@

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} Recent technological advances allow studying dynamic processes by computationally ordering single-cell omics profiles along a trajectory. Since 2014, at least 75 tools for trajectory inference have been developed. For end-users, however, these methods are difficult to execute and compare, mainly due to high variability in input/output data structures, software requirements, and programming interfaces. \\
	\textbf{Results:} We developed {dyno}, a toolkit for inferring, visualising and interpreting single-cell trajectories, giving access to more than 50 TI methods. {dyno} provides downstream analyses such as visualising the trajectory with dot-plots or heatmaps, automated labelling using gene sets, automated inference of the directionality, and detecting genes that are differentially expressed along the trajectory. \\
	\textbf{Conclusion:} By providing a uniform interface for executing and visualising trajectories of 50 methods, {dyno} allows inferring and comparing trajectories for a much broader audience than previously possible.
\end{quote}

@@

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} Network inference methods are computational tools which use large omics datasets to predict which genes are regulated by which transcription factors.
	Since regulatory interactions are context-dependent, attempting to model regulatory dynamics in the form of a single regulatory network may have little relevance. \\
	\textbf{Results:} In this work, we introduce {bred}, the first algorithm for inferring case-wise regulatory networks. We generate . Analysing case-wise regulatory networks of 14'963 profiles from The Cancer Genome Atlas project demonstrated that regulatory interactions are often specific to particular cancer types, but can also be shared between several cancer types. \\
	\textbf{Conclusion:} Ultimately, this analysis has resulted in a list of candidate oncogenic genes and interactions per cancer type, though further analysis and validation is required to confirm their oncogenicity.
\end{quote}
% TODO: fix abstract
\vfill
{\large \textbf{Publication status}}
\begin{quote}
	Manuscript in preparation. \\
	\textbf{Cannoodt R}, Saeys Y$^*$, and De Preter K$^*$. \\
	{\footnotesize $^*$ Equal contribution}
\end{quote}

@@

\ifrenderall
\newpage
\graphicspath{{./ch6_bred/}}
\include{ch6_bred/content}
\fi 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH8: INCGRAPH       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{incgraph: Optimising regulatory\\networks} 
\chaptermark{incgraph: Optimising regulatory networks.} % short title
\label{chap:incgraph}

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} Graphlets are small network patterns that can be counted in order to characterise the topology of a network. Counting graphlet can used to iteratively optimise a network in order to achieve certain topological properties.
	Hitherto graphlets were not suited as a metric for performing topology optimisation due to the computational complexity of recalculating all the graphlet counts for each of the edge modifications. \\
	\textbf{Results:} IncGraph calculates the differences in graphlet counts with respect to the network in its previous state, thereby reducing execution time by several orders of magnitude when compared to classic approaches.
	We demonstrate the usefulness of this approach optimising gene regulatory networks using a graphlet-based fitness score. \\
	\textbf{Conclusion:} IncGraph is able to quickly quantify the topological impact of small changes to a network, which opens novel research opportunities to study changes in topologies in evolving networks, or develop graphlet-based criteria for topology optimisation.
\end{quote}

@@

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} In computational biology and other sciences, researchers are frequently faced with a choice between several computational methods for performing data analyses. Benchmarking studies aim to rigorously compare the performance of different methods using well-characterized datasets, to determine the strengths of each method or to provide recommendations regarding suitable choices of methods for an analysis. However, benchmarking studies must be carefully designed and implemented to provide accurate, unbiased, and informative results. \\
	\textbf{Results:}  Here, we summarise key guidelines and recommendations for performing high-quality benchmarking analyses. Our review spans the full pipeline of benchmarking, from defining the scope to best practices for reproducibility. This includes crucial questions regarding design and evaluation principles. \\
	\textbf{Conclusion:} With this review, we aim to guide computational researchers in avoiding common pitfalls in designing, performing, and interpreting benchmarks.
\end{quote}

### 2019-12-10 ch3_dynbenchmark/content.tex
update

We generated a panel of toy datasets (using our \href{https://github.com/dynverse/dyntoy}{\textit{dyntoy}} package, \href{https://github.com/dynverse/dyntoy}{https://github.com/dynverse/dyntoy}) with all possible combinations of:

>>>>

We generated a panel of toy datasets (using our \href{https://github.com/dynverse/dyntoy}{\textit{dyntoy}} package, \url{https://github.com/dynverse/dyntoy}) with all possible combinations of:
